Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-15 paper/paper.qmd
Finished data evaluation in appendix

### Strengths and limitations
- what is good and bad about the sampling.

>>>>

### Strengths and limitations
Some strengths with The Washington Post's methodology is that they used the most comprehensive data out there about US homicides, which is the one from the FBI. Another strength about their methodology is that they addressed gaps in the data using court records for example and also validating the FBI's data with papers on homicide clearance rates and counts [@datahomicides]. However, a weakness of their sampling was the subjectivity surrounding the chose for the number of cities and why the largest 50 cities. Also another limitation with the sampling is that since their dataset is large, it is possible that the status of the homicide could have changed after they have finalized the dataset. Since @datahomicides are not directly asking police department for information, it is possible that the FBI could have left information out intentionally and it increases the complexity of their methodology to fill in the gap.
